### 2014-08-04 paper/paper.tex
Added labels. Wrote some for the intro and background. Stubed out some TODOs

July 29th, 2014 %TODO fix this

@@

\section{Introduction}

@@

\subsection{Specific Problem}

The focus of this undergraduate research project has been to preform sentiment
analysis in data from the microbloging website Twitter. All of the messages,
known as Tweets, are constrained in length to 140 characters. This limit forces
many users of Twitter to use abbreviations and contractions. This data presents
some interesting problems to performing good sentiment analysis due to it's
short and informal nature. Twitter makes it extremely easy to publish a Tweet
and has no way to edit a Tweet once published. This results in more spelling
mistakes and inconsistent grammar then other sources of text. Tweets often also
contain links to other websites in the form of URLs as well as taging system
for topics and other users.

\subsection{Task Description}

Organizers of the SemEval-2013 workshop created various sentiment analysis
tasks to be preformed. The task focused on for this project was task-2b:
Message polarity classification. The organizers used the Amazon service
``Mechanical Turk" to get many humans to annotate Tweets as `positive',
`negative' or `neutral'. In tweets with mixed sentiments, the prevailing
sentiment was chosen. Participants were tasked with creating a classifier to
establish labels for Tweets not in the training dataset. The various
submissions of the participants were then evaluated by the average of the
F-positive and the F-negative. The submissions were allowed categorized as
`unconstrained' or `constrained' depending on if they did or did not use
supplemental data, respectively.

\section{Background}

Quite a bit of research has been done in the field of sentiment analysis
recently. Much of the work has involved data from other contexts such as Movie
reviews \cite{Pang2002}, and blog posts \cite{Melville2009}. The challenges
associated with classifying Twitter data has attracted researchers in the past
few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.
Many previous attempts researched make use of Native Bayes, Maximum Entropy,
and SVM classifiers.

@@

\textit{Note: This section needs to be expanded. I am just not sure what else to write about...}

\section{Our Implementation}

\subsection{Summary of Maximum Entropy}

The Maximum Entropy classification method was focused on due to the limited
duration of the project. This supervised machine learning method calculates the
probability that a given document $d$ belongs to the class $c$.  The Maximum
Entropy approach is summarized below. For a more detailed description, see:
Nigam et al. \cite{Nigam1999}.

@@

\subsection{Preprocessing and Feature Selection}

@@

\subsection{Training Optimization}

@@

\section{Experiments and Discussion}

\subsection{Dataset}

@@

\subsection{Evaluation Measures}

@@

\subsection{Smooth Performance Measurement}

@@

\subsection{Number of features}

@@

\subsection{Baseline}

@@

\subsection{Experimental Results}

@@

@@

\subsection{Most Informative Features}

@@

\subsection{Comparison to Other Systems}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team       & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP  & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        NTNU       & 53.23 \\
        \textbf{Best MaxEnt}& \textbf{52.81} \\
        UoM        & 51.81 \\
        \textbf{Best Navie Bayes}& \textbf{50.96} \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$   & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}

\section{Conclusions and Future Work}

\subsection{Conclusions}

@@

\subsection{Future Work}

\subsubsection{Hashtags}

@@

\subsubsection{Users}

@@

\subsubsection{Support Vector Machine}

@@

\section{References}

@@

\section{Appendices}

\subsection{Running the Implementation}

@@

    \item \textbf{Install Prerequisites} - If \textit{python 2.7}, \textit{pip}, and \textit{flex} are not
        installed, they can be installed easily via a package manger:
\begin{Verbatim}[fontsize=\footnotesize]
sudo apt-get install python2.7 pip flex
\end{Verbatim}

Then various required python packages can be installed with:
\begin{Verbatim}[fontsize=\footnotesize]
sudo pip install -r
\end{Verbatim}
% TODO make requirement file

@@

    \item \textbf{Run the Program} - The classifier can be executed in a number of ways. There are two python programs that are executable: `conductor.py' and `crossval.py'. These two programs run the classifier in a simple fashion or with cross validation. There are a large number of command line arguments that can be viewed with:
\begin{Verbatim}[fontsize=\footnotesize]
python conductor -h
\end{Verbatim}

>>>>

August 4th, 2014 %TODO fix this

@@

\section{Introduction}
\label{section:intro}

@@

\subsection{Specific Problem}
\label{ssection:specificproblem}

The focus of this undergraduate research project has been to preform sentiment
analysis in data from the microbloging website Twitter. All of the messages,
known as Tweets, are constrained in length to 140 characters. This limit forces
many users of Twitter to use abbreviations and contractions. This data presents
some interesting problems to performing good sentiment analysis due to it's
short and informal nature. Twitter makes it extremely easy to publish a Tweet
and has no way to edit a Tweet once published. This results in more spelling
mistakes and inconsistent grammar then other sources of text. Tweets often also
contain URLs to other websites. Tweets also contain a certain amount of OOV
(Out-Of-Vocabulary) words, such as Hashtags, a tagging system for topics
allowing Tweets in a similar vein of conversation to be found. Other OOV words
include mentions (e.g. `@BarackObama') which are a method to direct a tweet to
one or more users, as well as `RT' which is an acronym for `retweet'
communicating that this particular Tweet is a reissuing of another users Tweet.
Another issue that is out of the scope of this project is that Twitter
currently supports 35+ languages, meaning that in-order to determine the
sentiment most systems must first determine which language the tweet is in.

\subsection{Task Description}
\label{ssection:taskdescription}

Organizers of the SemEval-2013 workshop created various sentiment analysis
tasks to be preformed. The task focused on for this project was task-2b:
Message polarity classification. The organizers used the Amazon service
``Mechanical Turk" to get many humans to annotate English language Tweets as
`positive', `negative' or `neutral'. In Tweets with mixed sentiments, the
prevailing sentiment was chosen. Participants were tasked with creating a
classifier to establish labels for Tweets not in the training dataset. The
various submissions of the participants were then evaluated by the average of
the F-positive and the F-negative. The submissions were allowed categorized as
`unconstrained' or `constrained' depending on if they did or did not use
supplemental data, respectively.

\section{Background}
\label{section:background}

Quite a bit of research has been done in the field of sentiment analysis
recently. Much of the work has involved data from other contexts such as Movie
reviews \cite{Pang2002}, and blog posts \cite{Melville2009}. The challenges
associated with classifying Twitter data has attracted researchers in the past
few years \cite{Jianfeng2013} \cite{Barbosa2010} \cite{Gokulakrishnan2012}.
Sentiment analysis has been very closely linked with opinion mining, which is
the practice of extracting sentiment on a particular topic in order to gain
insights into public opinion on the topic.

According to `Opinion mining and sentiment analysis' \cite{Pang2008}: ``The
year 2001 or so seems to mark the beginning of widespread awareness of the
research problems that sentiment analysis and opinion mining raise''. This
explosion in research has happened very recently, and as such the field is
moving very quickly.

Many previous attempts researched make use of Naive Bayes, Maximum Entropy, and
SVM classifiers. The Naive Bayes classifier uses the occurrences of features in
the \textit{training set} to calculate the probability that an example in the
\textit{test set} belongs in a given class. This method has the benefit of
linear time training since there is no iterative process, but I makes the
assumption that all features are independent, which is not the case in natural
language. The Maximum Entropy approach is explained in detail in section
\ref{ssection:summaryofmaxent}.

@@

\section{Our Implementation}
\label{section:implementation}

\subsection{Summary of Maximum Entropy}
\label{ssection:summaryofmaxent}

The Maximum Entropy classification method was focused on due to the limited
duration of the project, however a Naive Bayes classifier was also implemented
to provide a point of comparison. This supervised machine learning method
calculates the probability that a given document $d$ belongs to the class $c$.
The Maximum Entropy approach is summarized below. For a more detailed
description, see: Nigam et al. \cite{Nigam1999}.

@@

\subsection{Preprocessing and Feature Selection}
\label{ssection:featureselection}

% TODO expand on document frequency

@@

\subsection{Training Optimization}
\label{ssection:optimization}

@@

\section{Experiments and Discussion}
\label{section:experiments}

\subsection{Dataset}
\label{ssection:dataset}

@@

%TODO add example

\subsection{Evaluation Measures}
\label{ssection:evaluation}

@@

\subsection{Improving Performance Measurement}
\label{ssection:performancemeasurement}

@@

\subsection{Number of features}
\label{ssection:numfeatures}

@@

\subsection{Baseline}
\label{ssection:baseline}

@@

\subsection{Experimental Results}
\label{ssection:results}

%TODO write something here about the method

@@

% TODO Write something here about uncommon not getting performance gains
% without normalization

@@

\subsection{Most Informative Features}
\label{ssection:informativefeatures}

@@

\subsection{Comparison to Other Systems}
\label{ssection:comparison}

@@

\begin{table}[H]
    \begin{center}
    \begin{tabular}{|r|l|}
        \hline
        Team       & F \\
        \hline
        NRC-Canada & 69.02 \\
        GU-MLT-LT  & 65.27 \\
        teragram   & 64.86 \\
        BOUNCE     & 63.53 \\
        KLUE       & 63.06 \\
        AMI\&ERIC  & 62.55 \\
        FBM        & 61.17 \\
        AVAYA      & 60.84 \\
        SAIL       & 60.14 \\
        UT-DB      & 59.87 \\
        FBK-irst   & 59.76 \\
        nlp.cs.aueb.gr & 58.91 \\
        UNITOR     & 58.27 \\
        LVIC-LIMSI & 57.14 \\
        Unigon     & 56.96 \\
        NILC\_USP  & 56.31 \\
        DataMining & 55.52 \\
        ECNUCS     & 55.05 \\
        nlp.cs.aueb.gr & 54.73 \\
        ASVUniOfLeipzig & 54.56 \\
        SZTE-NLP   & 54.33 \\
        CodeX      & 53.89 \\
        Oasis      & 53.84 \\
        NTNU       & 53.23 \\
        \textbf{Best MaxEnt}& \textbf{52.81} \\
        UoM        & 51.81 \\
        \textbf{Best Navie Bayes}& \textbf{50.96} \\
        SSA-UO     & 50.17 \\
        SenselyticTeam & 50.10 \\
        $\ldots$   & $\ldots$ \\
        9 more teams &  \textless\ 50 \\
        \hline
        Majority Baseline & 29.19 \\
        \hline
    \end{tabular}
    \end{center}
    \caption{Comparison of constrained classifiers sumitted to the SemEval-2013
        workshop. Sorted by F-score.}
    \label{table:comparison}
\end{table}
%TODO fix this table

\section{Conclusions and Future Work}
\label{section:conclusionsandfuturework}

\subsection{Conclusions}
\label{ssection:conclusions}

@@

\subsection{Future Work}
\label{ssection:futurework}

\subsubsection{Hashtags}
\label{sssection:hashtags}

@@

\subsubsection{Users}
\label{sssection:users}

@@

\subsubsection{Support Vector Machine}
\label{sssection:svm}

@@

\section{References}
\label{section:referances}

@@

\section{Appendices}
\label{section:appendices}

\subsection{Running the Implementation}
\label{ssection:runningtheimplementation}

@@

    \item \textbf{Install Prerequisites} - If \textit{python 2.7},
        \textit{pip}, and \textit{flex} are not installed, they can be
        installed easily via a package manger:

\begin{Verbatim}[fontsize=\footnotesize]
sudo apt-get install python2.7 pip flex
\end{Verbatim}

Then various required python packages can be installed with:

\begin{Verbatim}[fontsize=\footnotesize]
sudo pip install numpy nltk
\end{Verbatim}

@@

    \item \textbf{Run the Program} - The classifier can be executed in a number
        of ways. There are two python programs that are executable:
        `conductor.py' and `crossval.py'. These two programs run the classifier
        in a simple fashion or with cross validation. There are a large number
        of command line arguments that can be viewed with:

\begin{Verbatim}[fontsize=\footnotesize]
python conductor -h
\end{Verbatim}
